An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-02-25 EconGrowth.Rnw
Now correctly including the effect of fixed gamma on the Cobb-Douglas with energy model for South Africa.

# print(iEGamma)

@@

# print(dataTable)
      # Now fit the CD model with fixed gamma

@@

@@

      model <- iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^(1 - alpha) * iEGamma

@@

gammaGrid <- seq(0.0, 1.0, by=0.1)
models <- cdGrid("US", "Q", gammaGrid)
SSE <- lapply(models, function(model) summary(model)$sigma)
data <- cbind(gammaGrid, SSE)
print("US")
plot(gammaGrid, SSE)
print(coef(models[[2]]))

>>>>

@@

      # We already know the value of gamma. We don't want to estimate it.
      # Establish guess values for lambda and alpha.

@@

      alphaGuess <- 0.7*(1-gamma) #ensure a consistent starting point.

@@

      model <- iGDP ~ exp(lambda*iYear) * iCapStk^alpha * iLabor^((1-gamma) - alpha) * iEGamma

@@

gammaGrid <- seq(0.05, 0.95, by=0.1)
models <- cdGrid("US", "Q", gammaGrid)
SSE <- lapply(models, function(model) summary(model)$sigma)
data <- cbind(gammaGrid, SSE)
print("US")
plot(gammaGrid, SSE)
print(coef(models[[2]]))
